---
title: "Notes"
author: "JC"
date: "9/8/2017"
output: html_document
---

```{r setup, include=TRUE,echo=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE,warning=FALSE)
```



## Why?
Save some time.
Quick & Dirty model diagnostic plots in ggplot.


## Plan

1. Redo base plots in ggplot

```{r, fig.align='center'}
par(mfrow=c(2,3))
lm.1 <- lm(mpg ~ wt,data=mtcars)
plot(lm.1,which=1:6)

```

2. Create ggplot versions ~ make tidy

```{r Diag1, echo=TRUE, collapse=TRUE,fig.align='default',eval=FALSE}
library(tidyverse)
library(broom)

My.Mod <- lm.1

#Base
plot(My.Mod,which=1)

#GGplot
D1  <- augment(My.Mod) %>% ggplot(aes(x=.fitted,y=.std.resid)) +
  geom_point() + 
  geom_smooth(se=FALSE,colour="red",size=.25) +
  geom_hline(yintercept=0,linetype=3) +
  labs(title="Residuls vs Fitted",subtitle=My.Mod$call)

D1
```

```{r ,ref.label=c("Diag1"),eval=TRUE,echo=FALSE, fig.align='default', fig.height=4,fig.width=4.5 }

```


3. Functionalise

How to determine models?  
What sort of arguments, functionality?  
PAss through   
Design ?    
```{r ,eval=FALSE}
## What should it look like?

# Pehaps???

MyModel %>% ggdiag()

Data %>% MyModel %>% ggdiag()

# plot index no or rather name?
Data %>% MyModel %>% ggdiag(Plot=1:2)
Data %>% MyModel %>% ggdiag(Plot=c("RVFit","qq"))


```


4. Ensure plays nice with existing


x. Other Thoughts  
Practice with RProj, Git.  
Don't re-invent the wheel - just make quicker to change the flat.


## Questions ???  
Logic for text annotation? How determine cutoff.
Starting assumptiom? Start from a) model (eg lm) or b) tidy output of model

  
```{r}
# How do you see how current plot is coded?
# This doesnt help
plot
```


