---
title: " Diagnostic Plot Comparison"
author: "JC"
date: "9/9/2017"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Diagnostic Plot Comparison}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include=TRUE,echo=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE,warning=FALSE,warnings=FALSE,messages=FALSE)
```


## Note

Diagnostic plot comparisons from base and this package.

Some notes on plot comparisons.
axis scale/ aspect slightly different 
Text annotations logic ~ highlighting
"Wigglyness" of line different ~ slightly different parameter used.


Data & Libs
```{r Libs}
library(tidyverse)
library(broom)
library(gridExtra)

# Traditional Model
lm.1 <- lm(mpg ~ wt,data=mtcars)

# Generic name
My.Mod <- lm.1
# Tidy output
Tidy.Mod <- augment(My.Mod)

# Attributes
class(My.Mod)
attributes(My.Mod)
head(Tidy.Mod,4)
```


\newpage
## Plot1: Residules v Fitted

```{r D1, echo=TRUE, collapse=TRUE,fig.align='default',eval=FALSE}

# base diagnostic
plot(My.Mod,which=1)

# ggDiagnostic plot
D1  <- augment(My.Mod) %>% 
  ggplot(aes(x=.fitted,y=.std.resid)) +
  geom_point() +
  geom_smooth(se=FALSE,colour="red",size=.25) +
  geom_hline(yintercept=0,linetype=3,colour="blue") +
  geom_text(aes(label=ifelse((.std.resid>1*IQR(.std.resid)),.rownames,"")),
             hjust=-0.1,vjust=-0.1,size=2.5) +
  labs(title="Residuls vs Fitted",subtitle=My.Mod$call)

D1
```

```{r ,ref.label=c("D1"),eval=TRUE,echo=FALSE, fig.align='default', fig.height=3.5,fig.width=3.5 }

```

\newpage
## Plot2: Normal QQ
 
```{r D2, echo=TRUE, collapse=TRUE,fig.align='default',eval=FALSE}

# base diagnostic
plot(My.Mod,which=2)

# ggDiagnostic plot
D2  <- augment(My.Mod) %>% 
  ggplot(aes(sample=.fitted)) +
  stat_qq() +
  labs(title="Normal QQ",subtitle=My.Mod$call)
  

D2 

```

```{r ,ref.label=c("D2"),eval=TRUE,echo=FALSE, fig.align='default', fig.height=3.5,fig.width=3.5 }

```

\newpage
## Plot3: Scale Location
```{r D3, echo=TRUE, collapse=TRUE,fig.align='default',eval=FALSE}
# base diagnostic
plot(My.Mod,which=3)

# ggDiagnostic plot
D3  <- augment(My.Mod) %>% 
  ggplot(aes(x=.fitted, y=sqrt(abs(.std.resid)))) +
  geom_point()+
  labs(title="Scale Location",subtitle=My.Mod$call) + 
  geom_smooth(se=FALSE,colour="red",size=.25) 

D3


```

```{r ,ref.label=c("D3"),eval=TRUE,echo=FALSE, fig.align='default', fig.height=3.5,fig.width=3.5 }

```



\newpage

## Plot4: Cooks Distance
```{r D4, echo=TRUE, collapse=TRUE,fig.align='default',eval=FALSE}
# Cooks Distance
# base diagnostic
plot(My.Mod,which=4)

# ggDiagnostic plot
D4 <- augment(My.Mod) %>% 
  ggplot(aes(x=seq_along(.cooksd), y=.cooksd)) +
  geom_point(size = .75) +
  geom_col(width = .1) +
  geom_hline(yintercept=.2,linetype=4,colour="orange") +
  labs(title="Cooks Dist",subtitle=My.Mod$call) +
  geom_text(aes(label=ifelse((.cooksd>.2),.rownames,"")),
              hjust=-0.1,vjust=-0.1,size=2.5)

D4
```

```{r ,ref.label=c("D4"),eval=TRUE,echo=FALSE, fig.align='default', fig.height=3.5,fig.width=3.5 }

```

\newpage
# Plot5: Resid vs Leverage

```{r D5, echo=TRUE, collapse=TRUE,fig.align='default',eval=FALSE }

# Resid vs Leverage

# base diagnostic
plot(My.Mod,which=5)

# ggDiagnostic plot
D5 <- augment(My.Mod) %>% 
  ggplot(aes(x=.hat, y=.std.resid)) +
  geom_point(size=.75) +
  geom_hline(yintercept=0,linetype=3,colour="blue") +
  labs(title="Resid vs Leverage",subtitle=My.Mod$call)

D5

```

```{r ,ref.label=c("D5"),eval=TRUE,echo=FALSE, fig.align='default', fig.height=3.5,fig.width=3.5 }

```

\newpage
# Plot6: CooksSD vs Leverage

```{r D6, echo=TRUE, collapse=TRUE,fig.align='default',eval=FALSE}
# base diagnostic
plot(My.Mod,which=6)

# ggDiagnostic plot
D6 <- augment(My.Mod) %>% 
  ggplot(aes(x=.hat, y=.cooksd)) +
  geom_point() +
  labs(title="CooksD vs Leverage",subtitle=My.Mod$call) 

D6
```

```{r ,ref.label=c("D6"),eval=TRUE,echo=FALSE, fig.align='default', fig.height=3.5,fig.width=3.5 }

```

\newpage
#Panel
```{r D7, echo=TRUE, collapse=TRUE,fig.align='default',eval=FALSE}

#library(gridExtra)

D.Panel <- grid.arrange(D1, D2, D3, D4, D5, D6, ncol=2)
D.Panel
```

```{r ,ref.label=c("D7"),eval=TRUE,echo=FALSE, fig.align='default'}

```

\newpage
```{r}
par(mfrow=c(2,3))
plot(My.Mod,which=1:6)
```

